Kids Combination

### 2019-11-26 stats/kids_combination.Rmd
update age by month

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
    mutate(age = age_num - min(age_num))%>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)

 d%>%
  filter(check_age == F)%>%
  select(subid, subage,test_date,dob,age_num,check_age)

>>>>

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_num_month = round(age_num_month)/12,
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
    mutate(age = age_num - min(age_num),
           age_month = age_num_month - min(age_num_month))%>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)
